%
% Parameters
%

\ifdefined\fullversion
\else
\def\fullversion{1}    % 0 = conference version; 1 = full version
\fi

\ifdefined\cameraversion
\else
\def\cameraversion{0}    % 0 = long version; 1 = proceedings version
\fi

\def\showoverflow{1}   % 1 = show overflows
\def\allow{1}      % 0 = remove todo command
\def\anonymous{1}      % 1 = anonymous

%
% Document class 
%

\documentclass[envcountsame,runningheads,notitlepage]{llncs}


\ifnum\fullversion=1
\usepackage[a4paper, margin=1.5in]{geometry}
\setlength{\marginparwidth}{2.5cm}
\fi



%
% Custom header
%

\input{ZZ_header}

\DeclareRobustCommand{\michals}[2] {{\color{magenta}{$\big[$\scriptsize\textsf{Michal #1:}} #2$\big]$}}

\title{Insert Title}
\titlerunning{Insert Running Title}
\date{}

\ifnum\anonymous=0
\author{
	Coauthor Name\inst{1} \and
	Coauthor Name\inst{2}
}% Add author name here

\institute{Coauthor University\\
	\href{mailto:mail@mail.com}{mail@mail.com} \and
	Coauthor University\\
	\href{mailto:mail@mail.com}{mail@mail.com}
}  % Add institute here

\else
\author{} 
\institute{}
\fi

\begin{document}
	\title{Security Analysis of Modified Shamir's Secret Sharing Scheme}
	
	\author{Research Team}
	\maketitle
	
	\section{Problem Definition}
	In Mnemonics project we use a modified version of Shamir's Secret Sharing Scheme (SSS) \cite{Shamir79} which can be stated as below. 
	
	\begin{definition}\label{def:shamir}
		Let $\FF_q$ be a finite field with $q$ elements and $t,n \in \ZZ$. A $(t, n)$-thresholds secret sharing scheme shares a secret $s \in \FF_q$ among $n$ users such that any $t$ or more shares can reconstruct the secret but $t-1$ or less cannot. Shamir's secret sharing scheme is an ideal and perfect A $(t, n)$-thresholds scheme and can be defined in two phases as follows:
		
		\begin{enumerate}
			\item \textbf{Share Generation Phase:} 
			\begin{enumerate}
				\item A dealer chooses a secret polynomial $f (x)$ with degree $t - 1$.
				\begin{equation*}
				f (x) = a_{t-1}x^{t-1} + \ldots + a_1x + a_0 \in \FF_q [x]
				\end{equation*}
				where $a_0 = s$, and $a_i \in_{R} \FF_q$ for $i = 1, \ldots, t-1$. 
				\item The dealer sends the tuple $(x_{i}, f (x_{i}))$ as the share to $i$-th user, where $x_{i} \in \FF_q$ are all non-zero and distinct for $i = 1, \ldots, n$. 
			\end{enumerate}
			
			\item \textbf{Reconstruction Phase:} 
			If any $t$ or more users jointly perform a Lagrange interpolation with their shares, they obtain the secret polynomial $f (x)$, and $f(0)$ yields the secret $s$.
		\end{enumerate}
	\end{definition}
	
	In addition to the above definition, we also encode the digest of the secret as $f(-1)$ as stated in ``\textit{SLIP-0039 : Shamir's Secret-Sharing for Mnemonic Codes}''. Our modified scheme is as follows:
	\begin{enumerate}
		\item \textbf{Share Generation Phase:}  
		\begin{enumerate}
			\item Let $s \in \FF_q$ be the secret to be shared and $D \in \FF_q$ be it's digest such that 
			\begin{equation*}
			D = \hsha2(R,s)[:d] \concat R
			\end{equation*} 
			\michals{13.03}{Please define a macro for the hash function, don't write \texttt{\textbackslash textrm\{HMAC-SHA256\}}}
			\ahmets{13.03}{done.}
			where $R$ is the randomness with length $m - d$ in bits for $m = \log_{2}{q}$ and some $d \in \ZZ$. In other words the digest share $D$ is composed of two parts; first $d$-bit part is the first $d$ bits of the output of the hash function and the remaining part is a randomness with $m - d$ bit length. Assume that we encode our secret as $s = f(0)$ and the digest $D = f(-1)$.
			\item Since we already have two points $(0, s)$ and $(-1, D)$, we sample random $t-2$ more points, i.e. $y_{1}, y_{2}, \ldots y_{t-2} \in_{R} \FF_q$.
			\item Using the above shares we perform Lagrange interpolation and construct the unique degree $t - 1$ polynomial $f (x)$ with respect to our points.  
			\item By evaluating $f (x)$ at the points $x_{t - 1}, \ldots x_{n}$ we generate $n - t + 2$ more shares.
			\item We output our shares as $(x_{i},y_{i})$ for $i = 1, \ldots n$.
		\end{enumerate}
		\item \textbf{Reconstruction Phase:}  
		\begin{enumerate}
			\item Recover the secret polynomial by applying Lagrange interpolation with $(x_{j}, y_{j})$ for $j = i_{1}, \ldots, i_{t}$.
			\item Compute the secret $s = f(0)$
			\item Compute the digest $D = f(-1)$
			\item If $\hsha(D[d:],s)[:d] = D[:d]$, then return $s$. Otherwise abort. 
		\end{enumerate}
	\end{enumerate}
	
	\iffalse
	\section{Security Analysis}
	Let $\adv$ be a PPT adversary holding $t-1$ shares among $n$. WLOG we can assume that $\adv$ has $(x_{i}, y_{i})$ for $i = 1, \ldots, t-1$. Lagrange interpolation formula tells us that constructing a degree $t - 1$ polynomial requires at least $t$ points. So $\adv$ has a missing point and let assume that this missing point be $(x_{t}, y_{t}) = (-1, D)$.
	
	The Lagrange interpolation formula is
	\begin{equation}\label{eq:Lag_int}
	f(x) = \sum\limits_{j = 1}^{t} y_{j} \ell_{j}(x),
	\end{equation}
	where $\ell_{j}(x)$ is the  Lagrange basis polynomial WRT the $j$-th point, i.e.
	\begin{equation}\label{eq:Lag_Basis}
	\ell_{j}(x) = \prod\limits_{\substack{k = 1 \\ k \neq j}}^{t} \frac{x - x_{k}}{x_{j} - x_{k}}.
	\end{equation}
	
	Since $\adv$ knows the $x$ coordinates of $t$ points she holds, she can compute the Lagrange basis polynomials according to (\ref{eq:Lag_Basis}). 
	
	Now, using (\ref{eq:Lag_int}) she writes
	
	\begin{align*}
	s &= f(0)\\
	&= \sum\limits_{j = 1}^{t-1} y_{j}\ell_{j}(0) + y_{t}\ell_{t}(0),
	\end{align*}
	and 
	\begin{equation}\label{eq:thelast}
	s - \sum\limits_{j = 1}^{t-1} y_{j}\ell_{j}(0) = y_{t}\ell_{t}(0).
	\end{equation}
	
	\michals{12.03.22}{That's not correct, we only have that the shares are not values at 0.} \ahmets{29.03}{Removed.}. Since the $x$ coordinates are all distinct, evaluation values of the Lagrange basis polynomials at zero are all non-zero. There exist one unknown in both sides of (\ref{eq:thelast}), i.e. $s$ and $y_{t}$. Since $s, y_{t} \in \FF_q$, for each possible value of $s \in \FF_q$ there exist a unique value $y_{t} \in \FF_q$. But Since $y_{t} = D$, $\adv$ can perform a brute-force attack on the secret $s$ and using (\ref{eq:thelast}) she eliminates the candidate secret giving invalid digest. More precisely $\adv$ can proceed as follows:
	
		\pcb{
		s' \sample \FF_q\\
		D' = \frac{s' - \sum\limits_{j = 1}^{t-1} y_{j}\ell_{j}(0)}{\ell_{t}(0)}\\
		\pcif D'[:d] \neq \hsha(R \concat s')[:d] \pcthen\\
		\t \text{Restart with a fresh $s'$}\\
		\pcelse\\
		\t \pcreturn s'}
	
	\michals{13.03}{There is no such a thing as "bruteforce space" for SSS -- this scheme is perfectly secure, i.e it remains secure even against unbounded adversaries}\ahmets{29.03}{Removed.}
	\michals{13.03.22}{please use macros from cryptocode}\ahmets{13.03}{done}
	\fi
	
	\section{Formal Security}
	First we prove the security of the original scheme.	
	Let $\FF_{q}$ be an extension field where $q = 2^{m}$ for some $m \in \ZZ$. 
	Let $\sP_{s}^{t - 1}$ be the set of all polynomials over $\FF_{q}$ with constant term $s$ and degree $t - 1$.
	The number of elements of $\sP_{s}^{t - 1}$ is exactly $q^{t-1}$. 
	We define an algorithm $\sdv$ which takes $n, t \in \ZZ$ and the secret $s$ as inputs, where $n$ is the number of shares and $t$ is the threshold. 
	The algoritm $\sdv(s, n, t)$ works as follows:
	
		\pcb{
		f(x) \sample \sP_{s}^{t - 1}\\
		\pcreturn f(x_1), \ldots, f(x_n)}
	for distinct $x_i \in \FF_q^*$ and $i = 1, \ldots, n$.
	
	Now we will show that for a fixed set of $t-1$ shares, the values that secret $s \in \FF_q$ can take are uniformly distributed in $\FF_q$. 
	To this end, we fix $t-1$ shares $y_1, \ldots, y_{t-1} \in \FF_q$. Let  $I \subset \{1, \ldots, n\}$ be the set of indices of the fixed $t-1$ shares. 
	
	There is exactly one polynomial $f(x) \in \sP_{s}^{t - 1}$ that satisfies $f(0) = s$ and $f(x_{i}) = y_{i}$ for $i \in I$. \michals{29.03}{This is not well written. points $(x_i, y_i)$ determines $s$ while the above could be read as "any $s$ and set $(x_i, y_i)$ determine a single polynomial."}
	Therefore the probability that $\sdv(s, n, t)$ chooses $f(x)$ exactly $1/q^{t-1}$.
	Now assume that we have another secret $s'$ For the same fixed set of $t-1$ shares.  
	From the same discussion above we can say that there is exactly one polynomial $g(x) \in \sP_{s'}^{t - 1}$ that satisfies $g(0) = s'$ and $g(x_{i}) = y_{i}$ for every $i \in I$.
	Therefore, for distinct secrets $s,s' \in \FF_q$ we have exactly the same probabilities such that
	\begin{align*}
		\probsub{f(x) \sample {\sP_{s}^{t - 1}}}{f(x_1) = y_1, \ldots, f(x_{t-1}) = y_{t-1}} &= \probsub{g(x) \sample {\sP_{s'}^{t - 1}}}{g(x_1) = y_1, \ldots, g(x_{t-1}) = y_{t-1}} \\
		&= 1/q^{t-1}.
	\end{align*}
	
	In other words, for a fixed $t-1$ shares $y_1, \ldots, y_{t-1} \in \FF_q$, and a secret $s \in \FF_q$, there exist only one polynomial $f(x)$ with degree $t-1$, satisfying $f(x_i) = y_i$ for $i = 1, \ldots, t-1$ and $f(0) = s$.
	Since there exist a unique polynomial for every possible value of $s$ and the secret $s$ is an element of $\FF_q$, for every fixed $t-1$ shares, the secret can take exactly $|\FF_q|$ distinct values. 
	Namely, for a  degree $t - 1$ secret polynomial $f(x)$ and fixed $t-1$ points $(x_1, y_1), \ldots, (x_{t-1}, y_{t-1})$, such that $f(x_i) = y_i$, $x_i, y_i \in \FF_q$ and $x_i \neq 0$, all the possible values that the secret $s \in \FF_q$ can take, satisfying $f(0) = s$, are equiprobable, that is exactly $1/q$.  
	 
	Therefore any $\ppt$ adversary $\adv$ against the original scheme who holds $t-1$ shares cannot do anything better than a random guess whose probability is exactly $1/q = 1/2^m$.
	
	Now we move on our modified scheme. 	
	In the modified version, the digest share, e.i. $D = k \concat R$, is also encoded as $f(-1)$, where  $k$ is the first $d$ bits of the output of $\hsha(R, s)$ and $R$ is an $m - d$ bit randomness. 
	We define an algorithm $\bdv$ which takes $t-1$ shares $y_i$ for $i \in I$, threshold $t \in \ZZ$ and the length of partial digest $k \in \ZZ$ as inputs.
	The algoritm $\bdv(y_1, \ldots, y_{t-1}, t, k)$ outputs a candidate secret $s'$ as follows:
	
	\pcb{
		s' \sample \FF_q\\
		D' = \frac{s' - \sum\limits_{j = 1}^{t-1} y_{j}\ell_{j}(0)}{\ell_{t}(0)}\\
		\pcif D'[:d] \neq k \pcthen\\
		\t \text{Restart with a fresh $s'$}\\
		\pcelse\\
		\t \pcreturn s'}
	where $\ell_{j}(x)$ is the  Lagrange basis polynomial with respect to the $j$-th share.
	Given a fixed $k$, for each uniformly sampled $D \in \FF_q$ there exist exactly one randomness $R$.  
	Since the randomness $R$ belongs to $\{0,1\}^{2^{m - d}}$, the probability that the algorithm $\bdv$ returns the correct secret value is 
	
	\begin{equation*}
		\condprob{s = s', s' \leftarrow \bdv(y_1, \ldots, y_{t-1}, t, k)}{k \in \{0,1\}^{2^{d}}} = 1/2^{m - d}.
	\end{equation*}
	
	Suppose that the adversary $\adv$ against the original scheme has access to the algorithm $\bdv$.
	We already have the following probabilities:
	\begin{itemize}
		\item $\condprob{s' = s}{s' \sample \FF_q} = 1/2^{m}$,
		\item $\condprob{s' = s}{s' \leftarrow \bdv(y_1, \ldots, y_{t-1}, t, k)} = 1/2^{m - d}$.
	\end{itemize}
	
	 $\adv$ gives a random $k$ and a threshold $t$ along with the $t-1$ shares to $\bdv$ as inputs. 
	 $\bdv$ proceeds as defined above and eventually outputs a candidate secret $s'$.
	 Then $\adv$ use this $s'$ in order to guess the secret with probability $1/2^{m - d}$.
	%\section{Introduction}
	%\label{sec:introduction}
	%\input{tex_files/01_introduction}
	
	\bibliographystyle{alpha}
	\bibliography{cryptobib/abbrev3,cryptobib/crypto}
	
\end{document} 
